Data Recovery and Pulse Position Modulation with a Photon Number Resolving SNSPD

### 2023-10-24 manuscript.tex
overleaf update

Prior to the PPM demosntration, we collected data with multi-photon optical pulses repeatedly impinging on the detector at the same time with respect to a clock. This way, we study how the PNR effect in isolation is manifest in the timing measurements recorded at the low and high trigger levels. We label the measurements from the low (8~mV) and high (50~mV) trigger levels as $t_A$ and $t_B$ respectively. As shown in fig.~\ref{fig:waveform}, histograms of these arrival events are multimodal due to the PNR response. We first present a method for recovering a symmetric arrival time response function using the the slope measurement $\Delta t_{BA} = t_B - t_A$.

@@

\hypertarget{fig:slope_correction}{%
\begin{figure}
\centering
\includegraphics[width=0.75\textwidth]{./figs_03/slope_cancellation_light.pdf}
\caption[{PNR Slope Variation Analysis and Cancellation}]{\textbf{PNR Slope Variation Analysis and Cancellation} a) 2D histogram of RF pulse measurements. Through graphing slope $\Delta t_{BA}$ on the x-axis and arrival time $t_A$ on the y-axis, a series of groupings are visible that identify the discrete photon numbers detected.}
\label{fig:slope_correction}
\end{figure}
}

>>>>

Prior to the PPM demosntration, we collected data with multi-photon optical pulses repeatedly impinging on the detector at the same time with respect to a clock. This way, we study how the PNR effect in isolation is manifest in the timing measurements recorded at the low and high trigger levels. We label the measurements from the low (8~mV) and high (50~mV) trigger levels as $t_A$ and $t_B$ respectively. As shown in Fig.~\ref{fig:waveform}, histograms of these arrival events are multimodal due to the PNR response. We first present a method for recovering a symmetric arrival time response function using the the slope measurement $\Delta t_{BA} = t_B - t_A$.

@@

\hypertarget{fig:slope_correction}{%
\begin{figure}
\centering
\includegraphics[width=1\textwidth]{./figs_03/slope_cancellation_light.pdf}
\caption[{PNR Slope Variation Analysis and Cancellation}]{\textbf{PNR Slope Variation Analysis and Cancellation} a) 2D histogram of RF pulse measurements. Through graphing slope $\Delta t_{BA}$ on the x-axis and arrival time $t_A$ on the y-axis, a series of groupings are visible that identify the discrete photon numbers detected.}
\label{fig:slope_correction}
\end{figure}
}
